DATA 621 - Business Analytics and Data Mining

### 2020-12-01 Final_project/Final Project Paper - Group 2.Rmd
Some more cleanup of unused code and squish graphic to save space

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```
```{r loadLibraries}
library(knitr)
library(dplyr)
library(dtplyr)
library(stringr)
library(ggplot2)
library(scales)
library(corrplot)
library(data.table)
```
```{r loadData}
dataHeader <- "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/"
ca_path <- paste0(dataHeader, "CAvideos.csv")
us_path <- paste0(dataHeader, "USvideos.csv")
gb_path <- paste0(dataHeader, "GBvideos.csv")
fr_path <- paste0(dataHeader, "FRvideos.csv")
de_path <- paste0(dataHeader, "DEvideos.csv")
droppedFields <- c('description', 'thumbnail_link')
ca_set <- fread(ca_path, drop = droppedFields)
us_set <- fread(us_path, drop = droppedFields)
gb_set <- fread(gb_path, drop = droppedFields)
fr_set <- fread(fr_path, drop = droppedFields)
de_set <- fread(de_path, drop = droppedFields)
nobsUS <- nrow(us_set)
nobsCA <- nrow(ca_set)
nobsGB <- nrow(gb_set)
nobsFR <- nrow(fr_set)
nobsDE <- nrow(de_set)
nobsTot <- nobsUS + nobsCA + nobsGB + nobsFR + nobsDE
nobsTotP <- prettyNum(nobsTot, big.mark = ",")
nobsCAP <- prettyNum(nobsCA, big.mark = ",")
```

@@

```{r numLogDensities}
ggplot(fullSetN[measure != 'views'], aes(x = value, color = measure)) +
  geom_density(kernel = "epanechnikov") +
  facet_wrap(~ country) +
  ggtitle("Predictor Density (semi-log scale)") +
  scale_x_log10(label = scientific)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```
```{r loadLibraries}
library(knitr)
library(dplyr)
library(dtplyr)
library(stringr)
library(ggplot2)
library(scales)
library(data.table)
```
```{r loadData}
dataHeader <- "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/"
ca_path <- paste0(dataHeader, "CAvideos.csv")
us_path <- paste0(dataHeader, "USvideos.csv")
gb_path <- paste0(dataHeader, "GBvideos.csv")
fr_path <- paste0(dataHeader, "FRvideos.csv")
de_path <- paste0(dataHeader, "DEvideos.csv")
droppedFields <- c('description', 'thumbnail_link')
ca_set <- fread(ca_path, drop = droppedFields)
us_set <- fread(us_path, drop = droppedFields)
gb_set <- fread(gb_path, drop = droppedFields)
fr_set <- fread(fr_path, drop = droppedFields)
de_set <- fread(de_path, drop = droppedFields)
nobsUS <- nrow(us_set)
nobsCA <- nrow(ca_set)
nobsGB <- nrow(gb_set)
nobsFR <- nrow(fr_set)
nobsDE <- nrow(de_set)
nobsTot <- nobsUS + nobsCA + nobsGB + nobsFR + nobsDE
```

@@

```{r numLogDensities, fig.height=4.5, fig.width=8}
ggplot(fullSetN[measure != 'views'], aes(x = value, color = measure)) +
  geom_density(kernel = "epanechnikov") +
  facet_wrap(~ country) +
  ggtitle("Predictor Density (semi-log scale)") +
  scale_x_log10(label = scientific)
```
